SmartCheck: Automatic and Efficient Counterexample Reduction and Generalization

### 2014-04-29 paper/paper.tex
paper: add problem def.

\section{Introduction}\label{sec:intro}
The QuickCheck testing framework was a revolutionary step-forward in
type-directed random testing~\cite{qc,monadic}.  Originally designed for Haskell,
QuickCheck has been ported to other languages and is a now a widely-used testing
tool.  Because QuickCheck generates random values for testing, counterexamples
it finds may be substantially larger than a minimal counterexample.  In their
original QuickCheck paper~\cite{qc}, the authors report the following user
experience by Andy Gill:
%
\begin{quote}
Sometimes the counterexamples found are very large and it is difficult to go
back to the property and understand why it is a counterexample.
\end{quote}
%
\noindent
QuickCheck defines a type class \ttp{Arbitrary} that presents a method
\ttp{arbitrary} for generating random values of a given type.  Gill added another
method to the type class:
%
\begin{code}
smaller :: a -> [a]
\end{code}
%
\noindent
The purpose of \ttp{smaller} is to generate strictly smaller values, according
to some measure, from a given counterexample.  These new values are then tested
to attempt to find a smaller counterexample.  Today, \ttp{smaller} is called
\ttp{shrink}.

>>>>

\section{Introduction}\label{sec:intro}
The QuickCheck testing framework was a revolutionary step-forward in
type-directed random testing~\cite{qc,monadic}.  Originally designed for Haskell,
QuickCheck has been ported to other languages and is a now a widely-used testing
tool.  Because QuickCheck generates random values for testing, counterexamples
it finds may be substantially larger than a minimal counterexample.  In their
original QuickCheck paper~\cite{qc}, the authors report the following user
experience by Andy Gill:
%
\begin{quote}
Sometimes the counterexamples found are very large and it is difficult to go
back to the property and understand why it is a counterexample.
\end{quote}

That is, automated testing helps find a counterexample, but it may be a very
large counterexample.  We are left facing the \emph{shrinking problem}: assume
there exist a set of inputs $i_0, \ i_1, \ldots, \i_n$, such that for program
$P$ (modeled as a function mapping inputs to output) and property $\phi$,
$\phi(P(i_0, \ i_1, \ldots, \i_n))$ is false.  The shrinking problem is to find
the smallest set of inputs $i'_0, \ i'_1, \ldots, \i'_n$, according to some
measure, such that $\phi(P(i\_0, \ i\_1, \ldots, \i\_n))$ is also false.

In general, the problem too expensive to solve, since it requires showing that
for a set of failing inputs, there exist no strictly smaller inputs that also
cause the property to fail.  Such a demonstration requires exhaustive testing or
proof.  Solutions to the shrinking problem are therefore approximated to
efficiently discover sufficiently small inputs causing the input to fail.
Usually, the shrunk inputs are derived algorithmically (but perhaps
nondeterministically) from a known larger set of inputs resulting in failure,
and the inputs may not be minimal.

To address the shrinking problem, QuickCheck defines a type class
\ttp{Arbitrary} that presents a method \ttp{arbitrary} for generating random
values of a given type.  Gill added another method to the type class:
%
\begin{code}
smaller :: a -> [a]
\end{code}
%
\noindent
The purpose of \ttp{smaller} is to generate strictly smaller values, according
to some measure, from a given counterexample.  These new values are then tested
to attempt to find a smaller counterexample.  Today, \ttp{smaller} is called
\ttp{shrink}.
